\texttt{davos}: The Python package smuggler

### 2022-03-30 paper/main.tex
title page and metadata

@@

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Title/Name of your software}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{A. Author}

\address{Your institute, some address}

\begin{abstract}
%% Text of abstract 
% Ca. 100 words

@@

\begin{keyword}
%keyword 1 \sep keyword 2 \sep keyword 3

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

@@

\section*{Required Metadata}
\label{}

\section*{Current code version}
\label{}

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
\hline
C1 & Current code version &  \\
\hline
C2 & Permanent link to code/repository used for this code version &  \\
\hline
C3 & Code Ocean compute capsule & \\
\hline
C4 & Legal Code License   &  \\
\hline
C5 & Code versioning system used &  \\
\hline
C6 & Software code languages, tools, and services used &  \\
\hline
C7 & Compilation requirements, operating environments \& dependencies & \\
\hline
C8 & If available Link to developer documentation/manual &  \\
\hline
C9 & Support email for questions & \\
\hline
\end{tabular}
\caption{Code metadata (mandatory)}
\label{} 
\end{table}

\linenumbers

%% main text

\section{Motivation and significance}
\label{}

\section{Software description}
\label{}

\subsection{Software Architecture}
\label{}

\subsection{Software Functionalities}
\label{}

\subsection{Sample code snippets analysis (optional)}
\label{}

\section{Illustrative Examples}
\label{}

\section{Impact}
\label{}

\section{Conclusions}
\label{}

\section{Conflict of Interest}

\section*{Acknowledgements}
\label{}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References:
\bibliographystyle{elsarticle-num} 
\bibliography{main.bib}

>>>>

\usepackage[hidelinks]{hyperref}
\usepackage{breakurl}

@@

\begin{document}
\begin{frontmatter}

\title{\texttt{davos}: The Python package smuggler}
\author{Paxton C. Fitzpatrick}
\author{Jeremy R. Manning\corref{cor}}
\ead{Jeremy.R.Manning@Dartmouth.edu}
\cortext[cor]{Corresponding author}
\address{Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755}

% ------------------------------------------------------ ABSTRACT ------------------------------------------------------

\begin{abstract}
% Text of abstract 
% Ca. 100 words

@@

\begin{keyword}
Python \sep Jupyter Notebook \sep Google Colaboratory \sep Reproducibility \sep Package management \sep Pip install
\end{keyword}

@@

% ------------------------------------------------------ METADATA ------------------------------------------------------
\section*{Required Metadata}

\section*{Current code version}

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
\hline
C1 & Current code version &  v0.1.0 \\
\hline
C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos} \\
\hline
C3 & Code Ocean compute capsule & \\
\hline
C4 & Legal Code License & MIT \\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & Python, JavaScript, pip, IPython, Jupyter, Ipykernel, PyZMQ. Additional tools used for tests: pytest, Selenium, Requests, mypy, GitHub Actions \\
\hline
C7 & Compilation requirements, operating environments \& dependencies & Dependencies:~Python$>$=3.6, packaging, setuptools.~Supported OSes: MacOS, Linux, Unix-like.~Supported IPython environments: Jupyter notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors. \\
\hline
C8 & If available Link to developer documentation/manual & \url{https://github.com/ContextLab/davos\#readme} \\
\hline
C9 & Support email for questions & contextualdynamics@gmail.com \\
\hline
\end{tabular}
\caption{Code metadata}
\label{}
\end{table}

\linenumbers
%The permanent link to code/repository or the zip archive should include the following requirements:

%README.txt and LICENSE.txt.

%Source code in a src/ directory, not the root of the repository.

%Tag corresponding with the version of the software that is reviewed.

%Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.

% --------------------------------------------- MOTIVATION & SIGNIFICANCE ----------------------------------------------
\section{Motivation and significance}

%Introduce the scientific background and the motivation for developing the software.

%Explain why the software is important, and describe the exact (scientific) problem(s) it solves.

%Indicate in what way the software has contributed (or how it will contribute in the future) to the process of scientific discovery; if available, this is to be supported by citing a research paper using the software.

%Provide a description of the experimental setting (how does the user use the software?).

%Introduce related work in literature (cite or list algorithms used, other software etc.).

% ------------------------------------------------ SOFTWARE DESCRIPTION ------------------------------------------------
\section{Software description}
% Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact.

\subsection{Software Architecture}
% Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.

\subsection{Software Functionalities}
% Present the major functionalities of the software.

\subsection{Sample code snippets analysis (optional)}

% ----------------------------------------------- ILLUSTRATIVE EXAMPLES ------------------------------------------------
\section{Illustrative Examples}
% Provide at least one illustrative example to demonstrate the major functions.

% Optional: you may include one explanatory video that will appear next to your article, in the right hand side panel. (Please upload any video as a single supplementary file with your article. Only one MP4 formatted, with 50MB maximum size, video is possible per article. Recommended video dimensions are 640 x 480 at a maximum of 30 frames/second. Prior to submission please test and validate your .mp4 file at $ http://elsevier-apps.sciverse.com/GadgetVideoPodcastPlayerWeb/verification$. This tool will display your video exactly in the same way as it will appear on ScienceDirect.).

% ------------------------------------------------------- IMPACT -------------------------------------------------------
\section{Impact}

%\textbf{This is the main section of the article and the reviewers weight the description here appropriately}

%Indicate in what way new research questions can be pursued as a result of the software (if any).

%Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).

%Indicate in what way the software has changed the daily practice of its users (if so).

%Indicate how widespread the use of the software is within and outside the intended user group.

%Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).

% ---------------------------------------------------- CONCLUSIONS -----------------------------------------------------
\section{Conclusions}
% Set out the conclusion of this original software publication.

\section*{Funding}
Our work was supported in part by NSF grant number 2145172 to J.R.M. The content is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.

\section*{Declaration of Competing Interest}
We wish to confirm that there are no known conflicts of interest associated with this publication and there has been no significant financial support for this work that could have influenced its outcome.

\section*{Acknowledgements}

%---------------------------------------------------- BIBLIOGRAPHY -----------------------------------------------------
\bibliographystyle{elsarticle-num} 
\bibliography{main.bib}
